Modeling the Java Card API (or Interface?) in B

### 2012-03-27 trunk/papers/B2012-work/javacardAPIpaper.tex
some text on exceptions

Among the different components of the Java Card platform, the Java
Card API is the one without which no refinement into Java Card code
could be done.  Suppose, for instance, that we had the B abstract
machine of Fig.~\ref{fig:Bmachine}, which models a bus card with a
variable that controls balance and a operation to add credits to the
balance. This is simple example provides enough evidence of the
importance of having a B model of the Java Card API.  As all data in
it is implementable in C, for instance, and it is a deterministic
specification, B tools can directly generate code for it in C, and the
resulting code would be very similar to the original B machine.

@@

[[[ PARA SIMONE -> Por favor, coloque os exemplos sob a forma de listing. Fica mais fácil de editar, controlar o tamanho e conteúdo e fica mais legível.
Quanto ao código javacard, basta o da operação addcredit. Aliás, o nome não está batendo. Não verifiquei o resto. Por favor verifique. ]]]

@@

@@

\section{Conclusions}

>>>>

Among the different components of the Java Card platform, the Java
Card API is the one without which no refinement into Java Card code
could be done.  Suppose, for instance, that we had the B abstract
machine of Fig.~\ref{fig:Bmachine}, which models a bus card with a
variable that keeps track of the current credit the user has (\texttt{balance}) and an operation to add credits to this
balance (\texttt{add\_credit}!!! verificar). This simple example provides enough evidence of the
importance of having a B model of the Java Card API.  As all data in
it is implementable in C, for instance, and it is a deterministic
specification, B tools can directly generate code for it in C, and the
resulting code would be very similar to the original B machine.

@@

[[[ PARA SIMONE -> Por favor, coloque os exemplos sob a forma de listing. Fica mais facil de editar, controlar o tamanho e conteudo e fica mais legivel.
Quanto ao codigo javacard, basta o da operacao addcredit. Alias, o nome não esta batendo. Nao verifiquei o resto. Por favor verifique. ]]]

[[[ PARA SIMONE -> tambem precisamos com urgencia daquela anelise sobre o que muda da 2.2.2 para a 3 ]]]

@@

As previously stated,  we chose to model exception raising conditions as operation pre-conditions in the B models. For instance, if the Java Card specification states that a method should throw an exception in case a parameter array is empty, the pre-condition of the corresponding B operation will require that this parameter is not empty. The B method then requires that every call to that operation satisfies the operation's pre-condition. As a consequence, code that is formally generated using the B method and the Java Card API specification should never raise this specific exception, as it is statically proved that all calls to this operation are made with non-empty parameter arrays. Not all situations leading to exceptional conditions are modeled, however, as some of them depend on the Java Card Runtime Environment (JCRE) and its state, which has not yet been modeled, and some require a more detailed specification of the contents of some data and other internal behavior.

@@

\section{Conclusions and future work}

With the current level of abstraction of the model and the fact that the Java Card Runtime Environment (JCRE) has not been modeled, some
conditions which may lead to exception raising are not yet modeled. Being able to model them would make developed applications even more sure, as more static verification could be carried out. Continuation of this work then will enlarge the scope of the modeling to cope statically with a larger set of situations.
